---
title             : "The relationship between sleep and physical activity across the lifespan"
shorttitle        : "Sleep and physical activity across the lifespan"

author: 
  - name          : "Taren Sanders*"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "33 Berry St, North Sydney, NSW, Australia"
    email         : "Taren.Sanders@acu.edu.au"
  - name          : "Timothy Hartwig"
    affiliation   : "2"
  - name          : "James Conigrave"
    affiliation   : "3"
  - name          : "Borja del Pozo-Cruz"
    affiliation   : "4, 5, 6"
  - name          : "Philip Parker"
    affiliation   : "7"
  - name          : "Michael Noetel"
    affiliation   : "8"
  - name          : "Devan Antczak"
    affiliation   : "9"
  - name          : "Stuart Fairclough"
    affiliation   : "10"
  - name          : "Shona Halson"
    affiliation   : "11"
  - name          : "--- DATASET PROVIDERS TBD ---"
    affiliation   : "12"
  - name          : "Chris Londale"
    affiliation   : "13"

affiliation:
  - id            : "1"
    institution   : "Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia"
  - id            : "2"
    institution   : "School of Behavioural and Health Science, Australian Catholic University, North Sydney, Australia"
  - id            : "3"
    institution   : "Centre for Alcohol Policy Research, La Trobe University, Bundoora, Australia"
  - id            : "4"
    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark"
  - id            : "5"
    institution   : "Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain"
  - id            : "6"
    institution   : "Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain"
  - id            : "7"
    institution   : "Office of the Deputy Vice-Chancellor (Research and Enterprise), Australian Catholic University, North Sydney, Australia"
  - id            : "8"
    institution   : "School of Psychology, University of Queensland, Brisbane, Australia"
  - id            : "9"
    institution   : "School of Education, University of Wollongong, Wollongong, Australia"
  - id            : "10"
    institution   : "Department of Sport and Physical Activity, Edge Hill University, Ormskirk, United Kingdom"
  - id            : "11"
    institution   : "--- TBD ---"
  - id            : "13"
    institution   : "Office of the Provost, Australian Catholic University, North Sydney, Australia"

authornote: |
  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["references.bib"]
csl               : "bmj.csl"

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_docx
---

\renewcommand{\arraystretch}{0.7}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("R/utils.R")
options(warn = -1)
knitr::opts_chunk$set(out.width = "110%")
```

```{r load-libraries}
library(targets)
library(gt)
require(ggplot2)
library(papaja)
```

```{r load-targets, include=FALSE}
tar_load(references)
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables_by_age)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")
```

# Introduction

Sleep is an important determinant of population health [@luysterSleepHealthImperative2012]. 
The consequences of poor sleep are profound and include increased all-cause mortality [@huangSleepPhysicalActivity2022], cardiovascular disease [@kwokSelfReportedSleep2018], cancers [@maSleepDurationTotal2016], and poor mental health [@wakefieldLongitudinalAssociationsFamily2020].
Poor sleep is common: over 50% of children and adolescents [@wheatonShortSleepDuration2018] and 35% of adults [@liuPrevalenceHealthySleep2016] report less sleep than recommended.
Improving sleep should be a priority for public health policy and more safe and accessible strategies that promote sleep are needed [@klinePhysicalActivitySleep2021].
In adults, being physically active appears to improve both the quantity and quality of sleep [@kredlowEffectsPhysicalActivity2015] and the World Health Organisation recommends physical activity as a method to improve sleep in adults [@bullWorldHealthOrganization2020].
In children, adolescents, and older adults associations are unclear [@antczakPhysicalActivitySleep2020; @klinePhysicalActivitySleep2021; @langRelationshipPhysicalActivity2016] and guidelines do not currently support a role for physical activity to improve sleep.

Promoting physical activity may be an effective method to improve sleep across the lifespan but the published literature to date has at least two limitations that prevent firm conclusions to support health guidelines.
First, most studies have relied on self-report measures of sleep and physical activity [@antczakPhysicalActivitySleep2020; @klinePhysicalActivitySleep2021; @langRelationshipPhysicalActivity2016], which could confound associations and limit the precision of analyses designed to identify a dose-response relationship between physical activity and sleep.
Second, no study has collected data from a large sample that included participants across the lifespan.
Umbrella reviews [@klinePhysicalActivitySleep2021] and meta-analyses [@aielloEffectExerciseTraining2016; @antczakPhysicalActivitySleep2020; @bannoExerciseCanImprove2018; @bartelProtectiveRiskFactors2015; @edwardsAssessingImpactDiet2019; @gaoShorttermEfficacyMinimally2019; @iftikharComparativeEfficacyCPAP2017; @iftikharEffectsExerciseTraining2014; @janssenAssociationsScreenTime2020; @kredlowEffectsPhysicalActivity2015; @kwokSelfReportedSleep2018; @langRelationshipPhysicalActivity2016; @ledermanDoesExerciseImprove2019; @lins-filhoEffectExerciseTraining2020; @maSleepDurationTotal2016; @mendelsonObstructiveSleepApnea2018; @rubio-ariasEffectExerciseSleep2017; @stutzEffectsEveningExercise2019; @yangEffectsExerciseSleep2020; @yangExerciseTrainingImproves2012; @yangSedentaryBehaviorSleep2017] have provided some suggestive evidence about how physical activity as a means of improving sleep may vary across the lifespan.
However, their reliance on aggregated study-level effects limits the quality and scope of data that can be used to analyse the influence of age [@rileyUsingIndividualParticipant2023].
Individual participant data (IPD) analysis can overcome these limitations [@ioannidisNextgenerationSystematicReviews2017].

In this study we harmonised individual participant data (IPD) from activity monitor observations obtained from studies around the world.
The objective of this pooled IPD study was to investigate the relationship between device-measured physical activity and sleep across the lifespan.
We examined whether individuals who are more physically active have better sleep, whether age, sex, and socio-cultural factors moderate the association between physical activity and sleep, and whether there is a bidirectional association between physical activity and sleep. 

# Results

```{r}
n_participants <- length(unique(data_clean$participant_id))
weekday_table <- (data_clean$weekday) |> table()
weekday <- chisq.test(weekday_table)
weekday_res <- glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")
```

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r n_participants |> pretty()` unique participants.
Table \@ref(tab:demo-participants) shows demographic information for all participants.
Observations were not uniform across the days of the week `r weekday_res`.
There were fewer observations on Monday (z = `r weekday$stdres["Monday"]`) and Sunday  (z = `r weekday$stdres["Sunday"]`); and more on Wednesday (z = `r weekday$stdres["Wednesday"]`).
A table of study characteristics can be found in supplementary materials.

```{r demo-participants}
papaja::apa_table(demog_table,
  caption = "Participant characteristics",
  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {n_participants |> pretty()}"),
  landscape = TRUE,
  col_spanners = list("Age group" = c(2, 6))
)
```

## The effects of physical activity volume on sleep

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
There was no meaningful relationship between physical activity volume and sleep duration or sleep efficiency.
Physical activity volume and sleep onset had a very weak positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_by_age$sleep$data,
  caption = model_tables_by_age$sleep$caption,
  note = model_tables_by_age$sleep$note,
  col_spanners = model_tables_by_age$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume. The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero. These plots demonstrate exact turning points where the effects of PA volume change by age."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_volume), error = FALSE)
```

## The effects of physical activity intensity on sleep

We estimated how physical activity intensity affects sleep across different age groups
We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
We found no evidence that physical activity intensity is related to sleep duration, sleep efficiency, or sleep onset.
However, we did find evidence for an association between physical activity intensity and improved sleep regularity, which weakened as age increased.

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity. The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_intensity), error = FALSE)
```

## The effects of sleep duration on physical activity

We estimated the effect of sleep duration on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
As age increases, both physical activity volume and intensity decrease.
We found no evidence for an association between average sleep duration and physical activity volume.

```{r pa-outcomes}
papaja::apa_table(
  model_tables_by_age$physical_activity$data,
  caption = model_tables_by_age$physical_activity$caption,
  note = model_tables_by_age$physical_activity$note,
  col_spanners = model_tables_by_age$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration. The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_duration_lag), error = FALSE)
```

## The effects of sleep efficiency on physical activity

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
We did not find a relationship between physical activity volume and sleep efficiency.
However, there was a weak linear association between sleep efficiency and more intense physical activity.

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency. The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_efficiency_lag), error = FALSE)
```

## The effects of sleep onset on physical activity

We estimated the effect of sleep onset on physical activity by age
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
There were weak curvilinear relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset. The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_onset_lag), error = FALSE)
```

## The effects of sleep regularity on physical activity

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
There was a U-shaped relationship between sleep regularity and physical activity volume.
Participants with below-average sleep regularity tended to have average physical activity volume.
Increases in regularity above the average were linked to greater physical activity volume.
There was a linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
Greater sleep regularity was associated with greater physical activity the following day.

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity. The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_regularity_lag), error = FALSE)
```

\newpage

# References

<div id = "refs"></div>

\newpage
