---
title: "Untitled Draft"
author: "Report Author"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "..")
#setwd("..")
source("R/utils.R")
source("R/model_builder_RQ1.R")
```
```{r load-libraries}
library(targets)
library(gt)
require(ggplot2)
library(papaja)
```

```{r load-targets, include=FALSE}
tar_load(model_list)
tar_load(data_clean)
pretty <- function(x) format(x, big.mark = ",")
```

# Results

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants. Table \@ref(demo) shows demographic information. A table of study characteristics can be found in supplementary materials.

## The effects of physical activity on sleep

We explored the effects of physical activity on sleep (RQ1) using mixed-effects models. We estimated the effect of physical activity and age


## Model tables

```{r results = "asis"}

tables <- lapply(model_list, function(x) x$table)
sapply(seq_len(length(tables)), function(x){
  
  cat("## ", names(tables)[x])
  tables[[x]] |> 
    gt() |> 
    apa_style() |> 
    as_raw_html() |> 
    cat()
  
  cat("\\n")
  cat("\\n")
})

```




# Discussion

# Conclusion
