---
title             : "The relationship between sleep and physical activity across the lifespan"
shorttitle        : "Sleep and physical activity across the lifespan"

author: 
  - name          : "Taren Sanders*"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "33 Berry St, North Sydney, NSW, Australia"
    email         : "Taren.Sanders@acu.edu.au"
  - name          : "Timothy Hartwig"
    affiliation   : "2"
  - name          : "James Conigrave"
    affiliation   : "3"
  - name          : "Borja del Pozo-Cruz"
    affiliation   : "4, 5, 6"
  - name          : "Philip Parker"
    affiliation   : "7"
  - name          : "Michael Noetel"
    affiliation   : "8"
  - name          : "Devan Antczak"
    affiliation   : "9"
  - name          : "Stuart Fairclough"
    affiliation   : "10"
  - name          : "Shona Halson"
    affiliation   : "11"
  - name          : "--- DATASET PROVIDERS TBD ---"
    affiliation   : "12"
  - name          : "Chris Londale"
    affiliation   : "13"

affiliation:
  - id            : "1"
    institution   : "Institute for Positive Psychology and Education, Australian Catholic University, North Sydney, Australia"
  - id            : "2"
    institution   : "School of Behavioural and Health Science, Australian Catholic University, North Sydney, Australia"
  - id            : "3"
    institution   : "Centre for Alcohol Policy Research, La Trobe University, Bundoora, Australia"
  - id            : "4"
    institution   : "Department of Sport Science and Clinical Biomechanics, University of Southern Denmark, Odense, Denmark"
  - id            : "5"
    institution   : "Department of Physical Education, Faculty of Education, University of Cádiz, Cádiz, Spain"
  - id            : "6"
    institution   : "Biomedical Research and Innovation Institute of Cádiz (INiBICA) Research Unit, Puerta del Mar University Hospital, University of Cádiz, Cádiz, Spain"
  - id            : "7"
    institution   : "Office of the Deputy Vice-Chancellor (Research and Enterprise), Australian Catholic University, North Sydney, Australia"
  - id            : "8"
    institution   : "School of Psychology, University of Queensland, Brisbane, Australia"
  - id            : "9"
    institution   : "School of Education, University of Wollongong, Wollongong, Australia"
  - id            : "10"
    institution   : "Department of Sport and Physical Activity, Edge Hill University, Ormskirk, United Kingdom"
  - id            : "11"
    institution   : "--- TBD ---"
  - id            : "13"
    institution   : "Office of the Provost, Australian Catholic University, North Sydney, Australia"

authornote: |
  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["references.bib"]
csl               : "bmj.csl"

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_docx
---

\renewcommand{\arraystretch}{0.7}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("R/utils.R")
options(warn = -1)
knitr::opts_chunk$set(out.width = "110%")
```

```{r load-libraries}
library(targets)
library(gt)
require(ggplot2)
library(papaja)
```

```{r load-targets, include=FALSE}
tar_load(references)
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables_by_age)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")
```

# Introduction

Sleep is an important determinant of population health [@luysterSleepHealthImperative2012].
The consequences of poor sleep are profound and include increased all-cause mortality [@huangSleepPhysicalActivity2022], cardiovascular disease [@kwokSelfReportedSleep2018], cancers [@maSleepDurationTotal2016], and poor mental health [@wakefieldLongitudinalAssociationsFamily2020].
Poor sleep is common: over 50% of children and adolescents [@wheatonShortSleepDuration2018] and 35% of adults [@liuPrevalenceHealthySleep2016] report less sleep than recommended.
Improving sleep should be a priority for public health policy and more safe and accessible strategies that promote sleep are needed [@klinePhysicalActivitySleep2021].
In adults, being physically active appears to improve both the quantity and quality of sleep [@kredlowEffectsPhysicalActivity2015] and the World Health Organisation recommends physical activity as a method to improve sleep in adults [@bullWorldHealthOrganization2020].
In children, adolescents, and older adults associations are unclear [@antczakPhysicalActivitySleep2020; @klinePhysicalActivitySleep2021; @langRelationshipPhysicalActivity2016] and guidelines do not currently support a role for physical activity to improve sleep.

Promoting physical activity may be an effective method to improve sleep across the lifespan but the published literature to date has at least two limitations that prevent firm conclusions to support health guidelines.
First, most studies have relied on self-report measures of sleep and physical activity [@antczakPhysicalActivitySleep2020; @klinePhysicalActivitySleep2021; @langRelationshipPhysicalActivity2016], which could confound associations and limit the precision of analyses designed to identify a dose-response relationship between physical activity and sleep.
Second, no study has collected data from a large sample that included participants across the lifespan.
Umbrella reviews [@klinePhysicalActivitySleep2021] and meta-analyses [@aielloEffectExerciseTraining2016; @antczakPhysicalActivitySleep2020; @bannoExerciseCanImprove2018; @bartelProtectiveRiskFactors2015; @edwardsAssessingImpactDiet2019; @gaoShorttermEfficacyMinimally2019; @iftikharComparativeEfficacyCPAP2017; @iftikharEffectsExerciseTraining2014; @janssenAssociationsScreenTime2020; @kredlowEffectsPhysicalActivity2015; @kwokSelfReportedSleep2018; @langRelationshipPhysicalActivity2016; @ledermanDoesExerciseImprove2019; @lins-filhoEffectExerciseTraining2020; @maSleepDurationTotal2016; @mendelsonObstructiveSleepApnea2018; @rubio-ariasEffectExerciseSleep2017; @stutzEffectsEveningExercise2019; @yangEffectsExerciseSleep2020; @yangExerciseTrainingImproves2012; @yangSedentaryBehaviorSleep2017] have provided some suggestive evidence about how physical activity as a means of improving sleep may vary across the lifespan.
However, their reliance on aggregated study-level effects limits the quality and scope of data that can be used to analyse the influence of age [@rileyUsingIndividualParticipant2023].
Individual participant data (IPD) analysis can overcome these limitations [@ioannidisNextgenerationSystematicReviews2017].

In this study we harmonised individual participant data (IPD) from activity monitor observations obtained from studies around the world.
The objective of this pooled IPD study was to investigate the relationship between device-measured physical activity and sleep across the lifespan.
We examined whether individuals who are more physically active have better sleep, whether age, sex, and socio-cultural factors moderate the association between physical activity and sleep, and whether there is a bidirectional association between physical activity and sleep.

# Methods

We pre-registered all methods and analyses on the Open Science Framework (OSF) before data acquisition began (https://osf.io/ahd96).

## Data sources and data acquisition

We included data from studies, with any design, that used activity monitors and a 24-hour wear time protocol over a minimum of 4 days, including 1 weekend day.
Studies needed to have used research-grade accelerometers from which raw accelerations ($m/s^2$ or $mg$) could be obtained.
Studies could use any wear location for the accelerometer (hip, wrist, or thigh).

We identified potentially relevant studies by examining the reference lists of recent systematic reviews that explored the relationship between sleep and physical activity in children, adolescents, and adults [@antczakPhysicalActivitySleep2020; @kredlowEffectsPhysicalActivity2015; @langRelationshipPhysicalActivity2016].
We then used forward searching on potentially eligible studies [@hindeBidirectionalCitationSearching2015].
We also performed a literature search to identify accelerometry consortiums and individual studies.
We also searched trial registries (ANZCTR, ICTRP, ISRCTN) and the Open Science Framework for unpublished results, and we asked collaborators to help identify any additional studies.

We contacted chief investigators or consortium leads by email to request access to deidentified IPD.
To make the data acquisition manageable, we only invited studies with sample sizes larger than 400 participants.
Contributing investigators, or their university, signed a data transfer agreement.
The lead university's Research Ethics Committee granted permission for each study's data to be obtained and investigators transferred their deidentified data via a secure file-sharing system.

## Data harmonisation and outcomes 

All activity monitor data were harmonised by reprocessing raw accelerometer files using an open-source GGIR package in R to produce physical activity and sleep outcomes [@miguelesGGIRResearchCommunity2019; @vanheesEstimatingSleepParameters2018].
By reprocessing all raw accelerometer data we were able to generate outcomes that could be compared across studies, devices wear location, and populations [@rowlandsProvidingBasisHarmonization2019].
Data were reprocessed by the core research team, or by data contributors themselves using the GGIR package processing script provided by the core research team.
Reprocessed individual study datasets were then pooled into a single dataset.
A detailed description of the reprocessing method and decisions for specific accelerometer devices is available in an online supplementary file.

For sleep, GGIR produced the following metrics; total sleep time (minutes), sleep efficiency (percentage of time asleep within the sleep time window), sleep regularity (regularity of sleep and awake patterns on a day-to-day basis calculated as the sleep regularity index), and timing (time of sleep and awakening within the 24-hour time cycle).
We examined associations of individual sleep characteristics and physical activity [@matriccianiRethinkingSleephealthLink2018], but researchers are increasingly using sleep as a multidimensional construct with sleep health  [@beiMeanSystematicReview2016; @buysseSleepHealthCan2014; @lunsford-averyValidationSleepRegularity2018; @phillipsIrregularSleepWake2017].
Together, these sleep metrics can be used as indicators of sleep quality [@ohayonNationalSleepFoundation2017].

For physical activity, we used volume and intensity metrics proposed by @rowlandsMovingForwardAccelerometerAssessed2018.
These measures are 1) average accelerations (measure of volume) and 2) intensity gradients (measure of intensity distribution where the natural logs of time and intensity are used to produce a straight-line graph with the slope of the graph being the intensity gradient).
We used this approach to model the full continuum of physical activity intensity for our main analyses [@rowlandsEnhancingValueAccelerometerassessed2019] and avoid collapsing physical activity data into population-specific intensity categories which occurs when intensity cut-points are applied to accelerometer data [@rowlandsDatadrivenMeaningfulEasy2019].

For the purposes of translating physical activity data for interpretation and public health recommendations and for time-use based analyses we then determined; 1) the number of minutes spent in acceleration intensity bands in $50mg$ increments [@rowlandsMovingForwardAccelerometerAssessed2018], 2) the number of minutes spent in light and moderate to vigorous physical activity using age appropriate cut-points applied to the time in intensity bands data, and 3) the minimum acceleration measured for a range of different durations, this is the $MX$ metric where $X$ refers to the duration.
For example, $M60$ refers to the minimum acceleration for the most active 60 minutes of the day [@rowlandsEnhancingValueAccelerometerassessed2019].
All awake time will also be further categorised into bout lengths for sedentary, light, and moderate to vigorous physical activity bouts using the categories defined by @gabaHowShortSleepers2020.
After extracting sleep and physical activity, the remaining time within the 24-hour time cycle was classified as sedentary behaviour.
Non-wear time and abnormally high acceleration values will be detected using the data processing default setting [@vanheesSeparatingMovementGravity2013].
This data will be classified as missing and will be imputed using the accelerometer data from the same time interval on the remaining days of the week.

## Covariates and moderators 

The following individual participant data will be obtained when available; age, sex, height, weight, waist circumference, maturational status, socioeconomic status (SES), ethnicity, screen time, sleep medications, and medically diagnosed conditions known to affect sleep.
The country, city, time zone, daylight length, and season in which data were collected will also be obtained.

## Statistical analysis 

To reduce the risk of bias in secondary data analysis of IPD, we used a blind analysis approach [@westonRecommendationsIncreasingTransparency2019].
We developed and tested models on a 10% holdout subsample of the dataset.
When the analysis code was ready, we conducted the final analysis [@maccounBlindAnalysisHide2015].

We checked all data for implausibly low or high measurements which were excluded if they fall outside of ±4SD of the mean.
We assumed missing covariate and moderator data to be missing at random or completely at random and imputed these missing values using multiple imputation by chained equations to provide 50 imputed datasets.
We used Rubin's rule to combine the results from all imputed datasets into one single set of results.
For all analyses, we examined 95% confidence intervals and used P < 0.05 to assess for statistical significance.
We used R (version `r paste(R.Version()[c("major", "minor")], collapse = ".")`) for all data cleaning and analysis.
We report mean and 95% confidence intervals.
For categorical variables, percentages are reported.
We examined model diagnostics on all models (see supplementary materials).

To examine the relationship between sleep and physical activity (Research Questions 1-2) we fit mixed-effects models with random intercepts for study ID to account for the nesting of participants in studies [@curranIntegrativeDataAnalysis2009].
We predict each sleep indicator by each physical activity indicator controlling for sex, body mass index (BMI) and region.

## Protocol deviations

This paper addresses Hypotheses 1 and 2 from our registered protocol
We will address remaining hypotheses in future research.
To streamline our analysis and reduce redundancy, we made some changes to our protocol while working with the holdout data.

### Using Study ID as fixed effect

We initially planned to use Study ID as a fixed effect, given that our study selection was not random.
But, as we aimed for our findings to generalise to other studies, estimating random intercepts for Study ID is also appropriate.
This approach allows us to estimate coefficients across studies, rather than partialling out study effects entirely.
While this change lessened the strength of model intercepts, it did not significantly alter model slopes.
The results using Study ID as a fixed effect (i.e., those that align with the protocol) can be found in the supplementary materials.

### Sleep indicator variable

Our research examines various aspects of sleep: onset, duration, regularity, and efficiency.
We initially planned to merge these variables into a single indicator to simplify analysis.
However, no validated indicator existed which could be estimated from our measured variables. 
We decided against creating one, as we could not validate it with our data.
Consequently, our models illustrate the relationship between each aspect of sleep and physical activity, instead of describing a straightforward link between overall sleep quality and physical activity.

### Log transformation

We aimed to improve model diagnostics using log transformations.
Pilot analysis using holdout data revealed that while diagnostics improved on the log scale, these model predictions followed extreme exponential patterns near the edge of the data range when back-transformed.
Accordingly we do not use log transformations in the main paper, however these models can be found in supplementary materials.

## Patient and public involvement

Patients and members of the public were not involved in the design, analysis or interpretation of this IPD study using secondary data. Results of this study have broad public health interest, particularly policymakers. Findings from this study will be disseminated through institutional websites, press and media platform releases, and tailored messages to public health organisations and governing bodies. 

# Results

```{r}
n_participants <- length(unique(data_clean$participant_id))
weekday_table <- (data_clean$weekday) |> table()
weekday <- chisq.test(weekday_table)
weekday_res <- glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")
```

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r n_participants |> pretty()` unique participants.
Table \@ref(tab:demo-participants) shows demographic information for all participants.
Observations were not uniform across the days of the week `r weekday_res`.
There were fewer observations on Monday (z = `r weekday$stdres["Monday"]`) and Sunday  (z = `r weekday$stdres["Sunday"]`); and more on Wednesday (z = `r weekday$stdres["Wednesday"]`).
A table of study characteristics can be found in supplementary materials.

```{r demo-participants}
papaja::apa_table(demog_table,
  caption = "Participant characteristics",
  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {n_participants |> pretty()}"),
  landscape = TRUE,
  col_spanners = list("Age group" = c(2, 6))
)
```

## The effects of physical activity volume on sleep

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
There was no meaningful relationship between physical activity volume and sleep duration or sleep efficiency.
Physical activity volume and sleep onset had a very weak positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_by_age$sleep$data,
  caption = model_tables_by_age$sleep$caption,
  note = model_tables_by_age$sleep$note,
  col_spanners = model_tables_by_age$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume. The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero. These plots demonstrate exact turning points where the effects of PA volume change by age."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_volume), error = FALSE)
```

## The effects of physical activity intensity on sleep

We estimated how physical activity intensity affects sleep across different age groups.
We present the results controlling for sex, SES, and BMI, in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-intensity-fig).
We found no evidence that physical activity intensity is related to sleep duration, sleep efficiency, or sleep onset.
However, we did find evidence for an association between physical activity intensity and improved sleep regularity, which weakened as age increased.

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity. The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_intensity), error = FALSE)
```

## The effects of sleep duration on physical activity

We estimated the effect of sleep duration on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-duration-fig).
As age increases, both physical activity volume and intensity decrease.
We found no evidence for an association between average sleep duration and physical activity volume.

```{r pa-outcomes}
papaja::apa_table(
  model_tables_by_age$physical_activity$data,
  caption = model_tables_by_age$physical_activity$caption,
  note = model_tables_by_age$physical_activity$note,
  col_spanners = model_tables_by_age$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration. The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_duration_lag), error = FALSE)
```

## The effects of sleep efficiency on physical activity

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-efficiency-fig).
We did not find a relationship between physical activity volume and sleep efficiency.
However, there was a weak linear association between sleep efficiency and more intense physical activity.

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency. The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_efficiency_lag), error = FALSE)
```

## The effects of sleep onset on physical activity

We estimated the effect of sleep onset on physical activity by age
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-onset-fig).
There were weak curvilinear relationships where average sleep onset was linked to the highest levels of physical activity volume and intensity.
The U-shaped relationship between sleep onset and physical activity volume attenuated for older participants.

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset. The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_onset_lag), error = FALSE)
```

## The effects of sleep regularity on physical activity

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes) and Figure \@ref(fig:PA-by-sleep-regularity-fig).
There was a U-shaped relationship between sleep regularity and physical activity volume.
Participants with below-average sleep regularity tended to have average physical activity volume.
Increases in regularity above the average were linked to greater physical activity volume.
There was a linear relationship between sleep regularity and physical activity intensity which slightly attenuated with age.
Greater sleep regularity was associated with greater physical activity the following day.

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity. The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_regularity_lag), error = FALSE)
```

# Discussion

# Conclusion

\newpage

# References

<div id = "refs"></div>

\newpage
